Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis

### 2018-02-13 manuscript/06_figures_tables.Rmd
Revise manuscript build process
- Use `doc` as default output
- Remove figures (draw them separately; only use figure captions in
manuscript)
- Render tables using `knitr`, but at end of manuscript

# Results

```{r prepresults}
cachefile <- ".cache/mvtraits_results.rds"
results_all <- readRDS(cachefile)

max_ss <- max(sample_size$sample_size)

multi_summary <- results_all %>%
  filter(model_type %in% c("uni", "multi")) %>%
  mutate(
    mu_mean = map(data, c("mu", "Mean")) %>%
      map(~as_tibble(as.list(.))),
    mu_lo = map(data, c("mu", "2.5%")) %>%
      map(~as_tibble(as.list(.))),
    mu_hi = map(data, c("mu", "97.5%")) %>%
      map(~as_tibble(as.list(.)))
      ) %>%
  select(model_type:pft, mu_mean:mu_hi) %>%
  unnest(.sep = ".") %>%
  gather("variable", "value", -(model_type:pft), na.rm = TRUE) %>%
  separate(variable, c("stat", "param"), sep = "\\.") %>%
  spread(stat, value) %>%
  mutate(
    pft = factor(pft, abbr2pft) %>% forcats::lvls_revalue(pft2abbr),
    param = factor(param, both_params)
  )

hier_prep <- results_all %>%
  filter(model_type == "hier") %>%
  select(model_type:pft_type, data) %>%
  mutate(
    mu_vals = map(data, "mu_group"),
    pft = map(mu_vals, names),
    mu_df = map2(pft, mu_vals, ~tibble(pft = ..1, dat = ..2))
  ) %>%
  select(-data, -mu_vals, -pft) %>%
  unnest()

hier_summary <- hier_prep %>%
  mutate(
    mu_mean = map(dat, c("Mean")) %>%
      map(~as_tibble(as.list(.))),
    mu_lo = map(dat, c("2.5%")) %>%
      map(~as_tibble(as.list(.))),
    mu_hi = map(dat, c("97.5%")) %>%
      map(~as_tibble(as.list(.)))
      ) %>%
  select(model_type:pft, mu_mean:mu_hi) %>%
  unnest(.sep = ".") %>%
  gather("variable", "value", -(model_type:pft), na.rm = TRUE) %>%
  separate(variable, c("stat", "param"), sep = "\\.") %>%
  spread(stat, value) %>%
  mutate(
    pft = if_else(is.na(pft), "global", pft),
    pft = factor(pft, abbr2pft) %>% forcats::lvls_revalue(pft2abbr),
    param = factor(param, both_params)
  )

# Absolute comparison of means
means_dat <- multi_summary %>%
  filter(pft != "GLOB", !is.na(pft)) %>%
  bind_rows(hier_summary) %>%
  left_join(sample_size) %>%
  mutate(
    model_type = factor(model_type, c("uni", "multi", "hier")) %>%
      forcats::lvls_revalue(c("univariate", "multivariate", "hierarchical")),
    mass_area = factor(mass_area, c("mass", "area")),
  ) %>%
  mutate_at(
    c("mu_mean", "mu_lo", "mu_hi"),
    ~10 ^ .
  ) %>%
  filter(
    !(param %in% c("leaf_lifespan", "SLA") & mass_area == "area")
  )
```

## Estimates of PFT-level means

```{r meanvaluetable, results = "asis"}
## Write summary table
table_cap_mass <- paste(
  "Mean and 95\\% confidence interval of trait estimates",
  "for mass-normalized traits from the hierarchical model."
)
table_cap_area <- gsub("mass", "area", table_cap_mass)

censor <- function(rxp, pft, pfts, param, value) {
  if_else(grepl(rxp, param) & pfts %in% pft, "---", value)
}

table_dat <- means_dat %>%
  filter(
    model_type == "hierarchical",
    !(param %in% c("SLA", "leaf_lifespan") & mass_area == "area")
  ) %>%
  mutate(
    mu_lo = if_else(param == "Rdmass", mu_lo * 1000, mu_lo),
    mu_mean = if_else(param == "Rdmass", mu_mean * 1000, mu_mean),
    mu_hi = if_else(param == "Rdmass", mu_hi * 1000, mu_hi),
    mu_lo = if_else(param == "Rdarea", mu_lo * 1000, mu_lo),
    mu_mean = if_else(param == "Rdarea", mu_mean * 1000, mu_mean),
    mu_hi = if_else(param == "Rdarea", mu_hi * 1000, mu_hi),
    lo_f = formatC(mu_lo, digits = 3),
    mid_f = formatC(mu_mean, digits = 3),
    hi_f = formatC(mu_hi, digits = 3),
    value = sprintf("%s (%s,%s)", mid_f, lo_f, hi_f),
    value = censor("Vcmax|Jmax", "C4G", pft, param, value),
    value = censor("Rdmass", "ShDBo", pft, param, value),
    value = censor("Jmax_mass", c("NlEBo", "NlD"), pft, param, value),
    value = censor("Jmax_area", c("NlD"), pft, param, value)
  ) %>%
  select(pft, param, value) %>%
  mutate(
    param = factor(param, both_params) %>% 
      forcats::lvls_revalue(param_markdown_nounit[both_params]),
  )%>%
  spread(param, value) %>%
  arrange(pft)

table_dat %>%
  select(-matches("area")) %>%
  kable(caption = table_cap_mass, format = "latex",
        escape = FALSE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down"))
table_dat %>%
  select(-matches("mass")) %>%
  kable(caption = table_cap_area, format = "latex",
        escape = FALSE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down"))
```

(ref:mccap) Mean and 95% confidence interval on best estimates of traits for each plant functional type from the univariate, multivariate, and hierarchical models.
For leaf lifespan and SLA, results were not significantly different between the mass- and area-based models, so only results from the mass-based model are shown.
For some PFT-trait combinations, where large error bars resulting from the relatively uninformative priors are substantially larger than the variability among means, the $y$ axes are constrained to facilitate comparison.

```{r meancompare, fig.width=7, fig.height=7, fig.cap='(ref:mccap)'}
pclip <- function(p, pname, value, lim, hi = TRUE) {
  f <- ifelse(hi, `>`, `<`)
  if_else(p == pname & f(value, lim), lim, value)
}

plot_dat <- means_dat %>%
  mutate(
    #too_few = sample_size < 2,
    #mu_hi = if_else(too_few, NA_real_, mu_hi),
    #mu_lo = if_else(too_few, NA_real_, mu_lo),
    #mu_mean = if_else(too_few, NA_real_, mu_mean),
    irrelevant = grepl("Vcmax|Jmax", param) & pft == "C4G",
    mu_hi = if_else(irrelevant, NA_real_, mu_hi),
    mu_lo = if_else(irrelevant, NA_real_, mu_lo),
    mu_mean = if_else(irrelevant, NA_real_, mu_mean),
    ## TODO: Fix these in the prior and re-run
    mu_hi = pclip(param, "Vcmax_mass", mu_hi, 1.5),
    mu_hi = pclip(param, "Vcmax_area", mu_hi, 100),
    mu_hi = pclip(param, "Jmax_mass", mu_hi, 1.8),
    mu_hi = pclip(param, "Jmax_area", mu_hi, 150),
    mu_mean = pclip(param, "Jmax_area", mu_mean, 150),
    mu_hi = pclip(param, "Rdmass", mu_hi, 0.03),
    mu_mean = pclip(param, "Rdmass", mu_mean, 0.03),
    mu_lo = pclip(param, "Rdmass", mu_lo, 0.03),
    mu_hi = pclip(param, "Rdarea", mu_hi, 0.0025),
    mu_mean = pclip(param, "Rdarea", mu_mean, 0.0025),
    mu_lo = pclip(param, "Rdarea", mu_lo, 0.0025),
    mu_hi = pclip(param, "Parea", mu_hi, 0.285),
    #mu_lo = pclip(param, "Jmax_area", mu_lo, 40, FALSE),
    param = forcats::lvls_revalue(param, param_fancy_chr[both_params])
  )

p_means <- ggplot(plot_dat) +
  aes(x = interaction(model_type, pft),
      y = mu_mean, ymin = mu_lo, ymax = mu_hi,
      color = pft, shape = model_type) +
  geom_pointrange(size = 0.3) +
  facet_wrap(~param, scales = "free", ncol = 2,
              labeller = label_parsed) +
  scale_y_continuous() +
  scale_color_manual(values = pft_colors) +
  guides(
    shape = guide_legend(title = "Model type"),
    color = guide_legend(title = "PFT")
  ) +
  ylab("Trait estimate mean and 95% CI") +
  xlab("Model type and PFT") +
  theme_bw() +
  theme(
    text = element_text(size = 12),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid = element_blank()
  )
p_means
```

In general, leaf trait estimates from the univariate, multivariate, and hierarchical models were similar (Fig.\ \@ref(fig:meancompare)).
Where we observed differences between models, the largest were between the univariate and multivariate models, while the additional constraint from the hierarchical model tended to have a minimal effect on trait estimates.
Significant differences in trait estimates between univariate and multivariate models occurred even for traits with relatively large sample sizes, such as leaf nitrogen content.

Evergreen PFTs had by far the largest leaf lifespan, with the longest lifespan observed for temperate and boreal needleleaf evergreen species.
Meanwhile, all of deciduous species had lifespans shorter than 7 months.
Among deciduous species, lifespan was generally longer in warmer biomes than colder ones.

Across-PFT patterns in SLA and $N_{mass}$, $P_{mass}$, and $R_{d,mass}$ were similar.
Temperate broadleaved deciduous trees and shrubs generally had among the highest values of these traits, while temperate evergreen trees and shrubs had generally among the lowest.
However, none of these patterns were universal to all four traits.
For example, tropical evergreen trees had relatively high $N_{mass}$ and average SLA and $R_{d,mass}$, but among the lowest $P_{mass}$.
Similarly, temperate and boreal shrubs had higher $N_{mass}$ and $P_{mass}$ than any of the grasses, but comparable SLA.

Across-PFT patterns in $N_{area}$, $P_{area}$, and $R_{d,area}$ were different from their mass-normalized counterparts.
For example, tropical broadleaved evergreen and needleleaf evergreen trees had among the lowest $N_{mass}$ and $P_{mass}$ basis but among the highest $N_{area}$ and $P_{area}$, while the opposite was true of deciduous temperate trees and shrubs.
Species with N contents near the middle of the observed range did not shift as dramatically depending on type of normalization.

C3 grasses had both the highest $V_{c,max,mass}$ and $V_{c,max,area}$.
Compared to broadleaved trees, temperate needleleaved evergreen trees had lower $V_{c,max,mass}$ but higher $V_{c,max,area}$.
Among broadleaved trees, deciduous trees had higher $V_{c,max,mass}$ and slightly higher $V_{c,max,area}$ than evergreen trees.
Between the deciduous and evergreen tree PFTs, we observed no significant trend by climate zone.

C3 grasses and temperate needleleaved evergreen trees had the highest $J_{max,area}$, but temperate broadleaved deciduous trees had the highest $J_{max,mass}$.
All of the shrub PFTs had the lowest $J_{max,mass}$ but average or above-average $J_{max,area}$, while the opposite was true of broadleaved tropical PFTs.
Of the tree PFTs, needleleaved evergreen trees had the highest $J_{max,area}$ but the lowest $J_{max,mass}$.

We observed clear differences in the relative uncertainties of mean estimates with respect to sample size.
All of the high-latitude PFTs consistently had among the largest error bars around their mean estimates relative to other PFTs, while the traits with the largest uncertainties were dark respiration, $V_{c,max}$, and $J_{max}$.
For many of these trait-PFT combinations, the additional constraint from trait covariance provided by the multivariate and hierarchical models substantially reduced error bars, making it possible to compare estimates against those of other PFTs.
Our analysis of the relationship between model type, sample size, and estimate relative uncertainty found that this covariance-based constraint from the multivariate model both reduced uncertainty overall (lower intercept) and reduced the sensitivity of estimate uncertainty to sample size (lower slope) compared to the univariate model (Fig.\ \@ref(fig:civssamplesize)).
However, this analysis revealed no consistent significant benefit from the hierarchical model.

(ref:sscap) Relative uncertainty in PFT-level trait estimates as a function of sample size for each model type.
Lines represent linear models ($\log(y) = b_0 + b_1 \log(x)$) fit independently for each model type.
In general, differences in estimate uncertainty between the univariate and multivariate models were minimal at large sample sizes but increasingly important at low sample sizes.
However, differences in estimate uncertainty between the multivariate and hierarchical models were consistently negligible.

```{r "civssamplesize", fig.width=4.4, fig.height=3, fig.cap='(ref:sscap)'}
## Relative uncertainty
cv_dat <- means_dat %>%
  mutate(
    cv = abs((mu_hi - mu_lo) / mu_mean)
  ) %>%
  filter(sample_size > 1)

cv_mod <- cv_dat %>%
  group_by(model_type) %>%
  nest() %>%
  mutate(
    cvfit = map(data, ~lm(log10(cv) ~ log10(sample_size), data = .))
  )

cv_coef <- cv_mod %>%
  mutate(
    coef = map(cvfit, broom::tidy)
  ) %>%
  unnest(coef) %>%
  select(model_type, term, estimate) %>%
  spread(term, estimate) %>%
  "names<-"(c("model_type", "intercept", "slope")) %>%
  mutate(
    eqn = sprintf("'%s: '~log[10](y) == %0.2f - %0.2f~log[10](x)", model_type, intercept, abs(slope))
  )

cv_pred <- cv_mod %>%
  mutate(
    grid = map(data, modelr::data_grid, sample_size = seq(5, max_ss)),
    cvpred = map2(grid, cvfit, modelr::add_predictions)
  ) %>%
  unnest(cvpred) %>%
  mutate(cv = 10 ^ pred)

x_lims <- range(cv_pred$sample_size)
y_lims <- range(cv_pred$cv)

relative_ci <- ggplot(cv_dat) +
  aes(x = sample_size, y = cv, color = model_type) +
  geom_point(size = 0.5) +
  geom_line(data = cv_pred) +
  annotate("text", x = rep(2500, 3), y = c(1.4, 1.25, 1.1), 
           label = cv_coef$eqn, parse = TRUE, 
           size = 2, vjust = "right") +
  scale_x_continuous(trans = "log10") +
  coord_cartesian(xlim = x_lims, ylim = y_lims) +
  xlab("Sample size") +
  ylab("Relative width of 95% CI") +
  scale_color_brewer(type = "qual", palette = 2) +
  guides(color = guide_legend(title = "Model type")) +
  theme_bw() +
  theme(
    legend.position = c(0.85, 0.75),
    panel.grid = element_blank()
  )
relative_ci
```

## Trait correlation patterns among- and within-PFTs

(ref:stickcap) Pairwise trait mean and covariance estimates for all data pooled globally (black) and for each PFT (colored).
Covariance estimates not significantly different from zero ($p < 0.05$) are indicated by x symbols at the mean estimate.
$x$ and $y$ axes vary on a log scale, reflecting the fact that the model was fit using the base 10 log of all traits.
With the exception of leaf lifespan, pairwise covariances are consistent in direction but vary somewhat in magnitude between PFTs, and when comparing PFT-level and global estimates.
However, many pairwise covariances are not statistically significant, particularly (but not always) for undersampled traits and PFTs.

```{r stickpairs, fig.width = 5, fig.height = 5, fig.cap = '(ref:stickcap)'}
suppressPackageStartupMessages({
  library(mvtraits)
})
results_sub <- results_all %>%
  filter((model_type == "multi" & pft == "global") |
         (model_type == "hier"))
dat_list <- results_sub$data
names(dat_list) <- with(results_sub, paste(model_type, mass_area, sep = "_"))

stickplot_pairs(
  #mu_global_lower = dat_list$hier_mass$mu_global,
  #Sigma_global_lower = dat_list$hier_mass$Sigma_global,
  mu_global_lower = dat_list$multi_mass$mu,
  Sigma_global_lower = dat_list$multi_mass$Sigma,
  mu_group_lower = dat_list$hier_mass$mu_group,
  Sigma_group_lower = dat_list$hier_mass$Sigma_group,
  vars_lower = mass_params,
  group_names = pft2abbr[-1],
  vars_label = param_labels,
  unlog_axes = TRUE,
  #mu_global_upper = dat_list$hier_area$mu_global,
  #Sigma_global_upper = dat_list$hier_area$Sigma_global,
  mu_global_upper = dat_list$multi_area$mu,
  Sigma_global_upper = dat_list$multi_area$Sigma,
  mu_group_upper = dat_list$hier_area$mu_group,
  Sigma_group_upper = dat_list$hier_area$Sigma_group,
  vars_upper = area_params,
  col_group = pft_colors,
  cex_g = 1.2,
  lwd_g = 1,
  lty_g = 1,
  lwd_s = 1.3,
  par_plot = list(oma = c(0, 5, 3, 5), cex = 0.4),
  par_legplot = list(mar = c(0, 0, 0, 0)),
  par_legend = list(ncol = 5, x = "center", cex = 0.6),
  reorder_legend = TRUE
)
mtext("Mass-normalized", side = 2, cex = 0.7, line = 3)
mtext("Area-normalized", side = 4, cex = 0.7, line = 1)
```

For all traits except leaf lifespan, pairwise trait correlations were generally consistent in direction both globally and within each PFT (Fig.\ \@ref(fig:stickpairs)).
In particular, mass- and area-normalized traits were all positively correlated with each other and, respectively, positively and negatively correlated with SLA, both globally and within each PFT.
The same was generally true of correlations of mass-based traits with leaf lifespan, but correlations of leaf lifespan with area-normalized traits were more variable.
The correlation between $N_{area}$ and leaf lifespan was positive globally and for evergreen shrubs but negative for broadleaved deciduous trees and not significant for any other PFTs.
Similarly, the correlation between $P_{area}$ and leaf lifespan was positive for temperate broadleaved evergreen trees and needleleaved evergreen trees but negative for evergreen shrubs.
The correlation between leaf lifespan and $R_{d,area}$ significant and positive globally, but was not significant within any PFTs.
The correlations of leaf lifespan with $V_{c,max,area}$ and $J_{max,area}$ were negative for temperate broadleaved deciduous trees, but not significant for any other PFTs or globally.

A large number of pairwise trait correlations were not significant.
In some cases, this was driven by sample size (Fig.\ \@ref(fig:samplesize)).
For instance, needleleaved deciduous trees were often the only PFT for which a correlation was not statistically significant.
In other cases, though, PFTs with smaller sample sizes had significant pairwise correlations while PFTs with much larger sample sizes had none.
For example, tropical broadleaved evergreen trees were relatively well-sampled for all traits, but none of their traits were well correlated with leaf lifespan.
Meanwhile, temperate broadleaved evergreen trees had significant correlations between leaf lifespan and SLA, $P_{area}$, and $R_{d,area}$.
In general, we observed fewer significant trait correlations among area-normalized traits than mass-normalized traits.

```{r boxprep}
outdir <- "../output"
hier_mass_file <- tail(dir(outdir, "hier.mass.clm45", full.names = TRUE), 1)
hier_area_file <- tail(dir(outdir, "hier.area.clm45", full.names = TRUE), 1)
multi_mass_file <- tail(dir(outdir, "multi.mass.clm45", full.names = TRUE), 1)
multi_area_file <- tail(dir(outdir, "multi.area.clm45", full.names = TRUE), 1)

hier_summary_mass <- readRDS(hier_mass_file)[["summary_table"]] %>%
  mutate(mass_area = "mass")
hier_summary_area <- readRDS(hier_area_file)[["summary_table"]] %>%
  mutate(mass_area = "area")
multi_summary_mass <- readRDS(multi_mass_file)[["summary_table"]] %>%
  mutate(mass_area = "mass")
multi_summary_area <- readRDS(multi_area_file)[["summary_table"]] %>%
  mutate(mass_area = "area")

proc <- function(dat, hier = TRUE) {
  if (hier) {
    dat <- filter(dat, group != "global")
  } else {
    dat <- mutate(dat, group = "global")
  }
  dat <- dat %>%
    filter(variable == "Corr") %>%
    separate(index, c("xvar", "yvar"), sep = "\\.\\.") %>%
    mutate(
      pft = factor(group, abbr2pft) %>% forcats::lvls_revalue(pft2abbr)
    ) %>%
    select(mass_area, pft, xvar, yvar, Mean, `2.5%`, `97.5%`)
}

hsm <- proc(hier_summary_mass)
hsa <- proc(hier_summary_area)
msm <- proc(multi_summary_mass, FALSE)
msa <- proc(multi_summary_area, FALSE)
hs <- bind_rows(hsm, hsa, msm, msa)
```

(ref:corrbarscap) Mean and 95% CI on estimates of pairwise correlation coefficients
for all data pooled globally (dark grey) and for each PFT (colored).
For most PFT-trait pairs, correlations are mutually consistent in magnitude but vary in strength.

```{r corrbars, fig.width=7, fig.height=7, fig.cap='(ref:corrbarscap)'}
.zzz <- close.screen(all.screens = TRUE)
corr_bar <- function(dat, xvar, yvar, mass_area) {
  dp <- dat %>%
    filter(
      mass_area == !!mass_area,
      (xvar == !!xvar & yvar == !!yvar) | 
        (xvar == !!yvar & yvar == !!xvar),
    ) %>%
    arrange(pft) %>%
    mutate(color = c("grey25", pft_colors))
  x <- barplot(dp$Mean, col = dp$color, border = dp$color,
               ylim = c(-1, 1), axes = FALSE)
  arrows(x, dp[["2.5%"]], x, dp[["97.5%"]],
         length = 0.01, angle = 90, code = 3)
  box()
}

nv <- length(mass_params)
main_screens <- split.screen(rbind(c(0, 1, 0.2, 1), c(0, 1, 0, 0.2)))
par(mar = rep(0.1, 4), oma = c(0, 8, 1, 5), cex = 0.4)
screens <- split.screen(c(nv, nv), screen = main_screens[1])
for (i in seq_len(nv)) {
  for (j in seq_len(nv)) {
    k <- j + nv * (i - 1)
    screen(screens[k])
    if (i == j) {
      # Label
      plot(0:1, 0:1, type = "n", ann = FALSE, axes = FALSE)
      box()
      text(x = 0.5, y = 0.5, labels = param_labels[i], cex = 2)
    } else {
      if (j > i) {
        # Upper triangle
        mass_area <- "area"
        xvar <- area_params[j]
        yvar <- area_params[i]
      } else {
        # Lower triangle
        mass_area <- "mass"
        xvar <- mass_params[j]
        yvar <- mass_params[i]
      }
      corr_bar(hs, xvar, yvar, mass_area)
    }
    if (i == 2 && j == 1) {
      axis(side = 2)
    }
    if (i == 1 && j == nv) {
      axis(side = 4)
    }
  }
}
## Draw legend
screen(main_screens[2])
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
plot(0, 0, type = "n", axes = FALSE, ann = FALSE)
legend("center", legend = levels(hs$pft), fill = c("grey25", pft_colors), 
       ncol = 5, bty = "n")
close.screen(all.screens = TRUE)
mtext("Mass-normalized", side = 2, cex = 0.7, line = 1)
mtext("Mean and 95% CI of pairwise correlation", side = 2, cex = 1, line = 2)
mtext("Area-normalized", side = 4, cex = 0.7, line = 0)
```

The strength of pairwise trait correlations varied substantially depending on scale, PFT, and trait (Fig.\ \@ref(fig:corrbars)).
The two pairwise trait correlations that exhibited the most consistent strength globally and within each PFT were the correlation between SLA and $N_{area}$, and between $N_{mass}$ and $P_{mass}$.
Correlation strength was often, but not always, related to sample size, with well-sampled PFTs exhibiting stronger correlations and undersampled PFTs exhibiting weaker correlations.

>>>>

# Tables {-}

```{r "knitr_options", echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
library(knitr)
library(here)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE
)
options(knitr.table.format = "pandoc")
```

<!-- Tables ---------------------------->
```{r "read_chunks"}
knitr::read_chunk(here::here("scripts/manuscript-analyses/try_ref_table.R"))
knitr::read_chunk(here::here("scripts/manuscript-analyses/table_n_species.R"))
```

<!-- TRY data citations -->
```{r "trydata"}
```

<!-- Number of species in each PFT -->
```{r "pfts"}
```

# Figure captions {-}

**Figure 1**: Sample sizes for each trait-PFT pair. $y$ axis is scaled logarithmically.

**Figure 2**: Mean and 95% confidence interval on best estimates of traits for each plant functional type from the univariate, multivariate, and hierarchical models.
For leaf lifespan and SLA, results were not significantly different between the mass- and area-based models, so only results from the mass-based model are shown.
For some PFT-trait combinations, where large error bars resulting from the relatively uninformative priors are substantially larger than the variability among means, the $y$ axes are constrained to facilitate comparison.

**Figure 3**: Relative uncertainty in PFT-level trait estimates as a function of sample size for each model type.
Lines represent linear models ($\log(y) = b_0 + b_1 \log(x)$) fit independently for each model type.
In general, differences in estimate uncertainty between the univariate and multivariate models were minimal at large sample sizes but increasingly important at low sample sizes.
However, differences in estimate uncertainty between the multivariate and hierarchical models were consistently negligible.

**Figure 4**: Pairwise trait mean and covariance estimates for all data pooled globally (black) and for each PFT (colored).
Covariance estimates not significantly different from zero ($p < 0.05$) are indicated by x symbols at the mean estimate.
$x$ and $y$ axes vary on a log scale, reflecting the fact that the model was fit using the base 10 log of all traits.
With the exception of leaf lifespan, pairwise covariances are consistent in direction but vary somewhat in magnitude between PFTs, and when comparing PFT-level and global estimates.
However, many pairwise covariances are not statistically significant, particularly (but not always) for undersampled traits and PFTs.

**Figure 5**: Mean and 95% CI on estimates of pairwise correlation coefficients
for all data pooled globally (dark grey) and for each PFT (colored).
For most PFT-trait pairs, correlations are mutually consistent in magnitude but vary in strength.

# References {-}

### 2018-02-13 manuscript/index.Rmd
Revise manuscript build process
- Use `doc` as default output
- Remove figures (draw them separately; only use figure captions in
manuscript)
- Render tables using `knitr`, but at end of manuscript

---
title: "Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates"
author: >
  Alexey N. Shiklomanov$^1$,
  Elizabeth M. Cowdery$^1$,
  Michael Bahn$^2$,
  Chaeho Byun$^3$,
  Joseph Craine$^4$,
  Andrés Gonzalez-Melo$^5$,
  Alvaro G. Gutiérrez$^6$,
  Steven Jansen$^7$,
  Nathan Kraft$^8$,
  Koen Kramer$^{9}$,
  Vanessa Minden$^{10,11}$
  Ülo Niinemets$^{12}$,
  Yusuke Onoda$^{13}$,
  Enio Egon Sosinski$^{14}$,
  Nadejda A. Soudzilovskaia$^{15}$,
  Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands

Corresponding author:
Alexey Shiklomanov,
telephone: +1 (302) 897-3348,
email: ashiklom\@bu.edu

Key words: Functional trade-off; hierarchical modeling; trait variation; ecological modeling; leaf morphology; leaf biochemistry

```{r wordcount, echo = FALSE}
fnames <- c(
  introduction = "01_introduction.md",
  methods = "02_methods.Rmd",
  results = "03_results.Rmd",
  discussion = "04_discussion.md",
  conclusions = "05_conclusions.md"
)
files <- file.path(
  "~/Projects/new-phytologist-traits/np-trait-analysis/manuscript-md", 
  fnames
)
names(files) <- names(fnames)

>>>>

---
title: "Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis"
author:
  - >
    Alexey N. Shiklomanov$^1$
    Elizabeth M. Cowdery$^1$,
    Michael Bahn$^2$,
    Chaeho Byun$^3$,
    Joseph Craine$^4$,
    Andrés Gonzalez-Melo$^5$,
    Alvaro G. Gutiérrez$^6$,
    Steven Jansen$^7$,
    Nathan Kraft$^8$,
    Koen Kramer$^{9}$,
    Vanessa Minden$^{10,11}$,
    Ülo Niinemets$^{12}$,
    Yusuke Onoda$^{13}$,
    Enio Egon Sosinski$^{14}$,
    Nadejda A. Soudzilovskaia$^{15}$,
    Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::word_document2:
    toc: no
    reference_docx: ~/Projects/misc/pandoc-docx-template/academic-numbered.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
<div custom-style="Affiliation">
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
</div>

<div custom-style="Single space">
Corresponding author:

Alexey Shiklomanov,

telephone: +1 (302) 897-3348,

email: ashiklom\@bu.edu

Key words: Functional trade-off; hierarchical modeling; trait variation; ecological modeling; leaf morphology; leaf biochemistry
</div>

```{r wordcount, echo = FALSE}
fnames <- c(
  introduction = "01_introduction.md",
  methods = "02_methods.Rmd",
  results = "03_results.Rmd",
  discussion = "04_discussion.md",
  conclusions = "05_conclusions.md"
)
files <- here::here(
  "manuscript", 
  fnames
)
names(files) <- names(fnames)
